### 2015-07-05 narrative/enabling_tech.tex
minor edits

For this project, we plan to use the Sirocco data storage mechanism to
offer managing the actual data storage on all of the different tiers. We'll add
a data management layer as part of the file system to handle data discovery and
metadata tasks. As a middleware layer, we will investigate offering differing
data compression, fidelity, and storage placement options. Through this 
combination, we will be able to deliver a complete end-to-end system.

In this project we will extend ADIOS~\cite{adios} with new APIs and novel techniques
to coordinate with the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time. We will test our ideas on the next generation OLCF,
SNL/LANL, and NERSC systems.
%
We plan to leverage the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project and the Ceph storage system project (ceph.com).
In the LWFS project, Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, were added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has developed a usable storage infrastructure.

>>>>

For this project, we plan to use the Sirocco data storage mechanism to manage
the actual data storage on all of the different tiers. Our initial thought on
where the dividing line between the storage layer and the middleware is as
follows. We will add a data management functionality as part of the storage
system layer to handle data discovery and metadata tasks. At the middleware
layer, we will investigate offering differing data compression, fidelity,
storage placement, and retrieval selection options.  Through this combination,
we will be able to deliver a complete end-to-end system. We will investigate
which functionality works best at the different layers for usability and
scalability.

In this project we will extend ADIOS~\cite{adios} with new APIs and novel
techniques to coordinate with the storage back-end. The key idea is offering
the ability to negotiate with the storage system to agree on the tradeoff
between data quality and response time. We will test our ideas on the next
generation OLCF, SNL/LANL, and NERSC systems.

We plan to leverage the many inovations we discovered in the Lightweight File
Systems~\cite{lwfs} (LWFS) project and the Ceph~\cite{weil:osdi06} storage
system project.  In the LWFS project, Sandia sought to demonstrate stripping
down a file system to the bare minimum features required for any storage
system. Then, additional functionality and semantics, such as POSIX-style
directories and consistency requirements, were added in using auxiliary
services separate from the stack or by layering providing a new interface to
the storage system. The project's first phase demonstrated that using a core
object storage system with integrated security providing authentication and
authorization services, customized storage interfaces could be developed with
exactly the overhead required for different applications. The second phase of
LWFS, known as Sirocco~\cite{sirocco}, is investigating how to manage storage
devices for efficient and scalable storage performance.  Sirocco has been in
process for three years and has developed a usable storage infrastructure.
